%%\documentclass[manuscript]{biometrika}
%\documentclass[lineno]{biometrika}
\documentclass[letterpaper,11pt]{article}
%\usepackage[slantedGreek]{mathpazo}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage[top=8pc,bottom=8pc,left=8pc,right=8pc]{geometry}
%\usepackage{ntheorem}

%\usepackage{amssymb}
%\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{multirow}

%% Please use the following statements for
%% managing the text and math fonts for your papers:
\usepackage{times}
%\usepackage[cmbold]{mathtime}
\usepackage{bm}
\usepackage{natbib}
\usepackage[plain,noend]{algorithm2e}

%% For compressing some space: 
\setlength{\textfloatsep}{10pt plus 1.0pt minus 2.0pt}
\setlength{\floatsep}{12.0pt plus 2.0pt minus 5.0pt}
\setlength{\intextsep}{12.0pt plus 2.0pt minus 5.0pt}
\setlength{\belowcaptionskip}{-2pt}

%\setlength{\textheight}{9in}
%\setlength{\textwidth}{6in}
%\setlength{\topmargin}{-36pt}
%\setlength{\oddsidemargin}{0pt}
%\setlength{\evensidemargin}{0pt}

%\usepackage{array}
\include{math-commands}

\begin{document}

%\jname{Biometrika}
%%% The year, volume, and number are determined on publication
%\jyear{2016}
%\jvol{}
%\jnum{}
%%% The \doi{...} and \accessdate commands are used by the production team
%%\doi{10.1093/biomet/asm023}
%\accessdate{Advance Access publication on 31 July 2016}
%\copyrightinfo{\Copyright\ 2016 Biometrika Trust \goodbreak {\em Printed in Great Britain}}

%% These dates are usually set by the production team
%\received{April 2016}
%\revised{September 2016}

%% The left and right page headers are defined here:
\markboth{Bhadra, Datta, Polson, and Willard}{Global-Local Mixtures}

%% Here are the title, author names and addresses
\title{\vspace{-1cm} Global-Local Mixtures}

\author{Anindya Bhadra  \footnote{{\em Address:} 250 N. University St., West Lafayette, IN 47907, email: bhadra@purdue.edu.} \\Purdue University
\and Jyotishka Datta  \footnote{{\em Address:} Box 90251, Durham, NC 27708, email: jd298@stat.duke.edu.}\\ Duke University and SAMSI\\
\and Nicholas G. Polson \footnote{{\em Address:} 5807 S. Woodlawn Ave., Chicago, IL 60637, email: ngp@chicagobooth.edu.}  \ \ and Brandon Willard \footnote{{\em Address:} 5807 S. Woodlawn Ave., Chicago, IL 60637, email: brandonwillard@gmail.com.} \\The University of Chicago Booth School of Business}

\maketitle
\begin{abstract}
\noindent 
We show how to generate global-local mixtures using the \CS and the Liouville integral transformation identities. This leads to simpler characterizations of well-known normal-scale mixture distributions such as the Laplace or Lasso, the logit and the quantile. We also show how they lead to new probability distributions as global-local mixtures of appropriate baseline densities. Finally, we conclude with a conjecture concerning the Bayesian bridge and uniform correlation mixture of a bivariate normal density with unit variances. 
\end{abstract}

\noindent {\bf Keywords:}  
Global-local mixture, Scale mixture, Stable laws, Bayes regularization.

\section{Introduction}
%\section{Global-Local Mixtures}
Many statistical problems involve regularization penalties that can be viewed as global-local mixture prior distributions \citep{polson2011data, hans2011comment}. A $p$-dimensional random variable $X = (x_1, \ldots, x_p)^{\T}$ is said to have a global-local mixture distribution if we can write its marginal probability density function as: 
\begin{align*}
p(x_i) & = \int_{0}^{\infty} p(x_i \mid \tau) p(\tau) d\tau \text{ where, }\\
p( x_i \mid \tau) & = \int_{0}^{\infty} p(x_i \mid \lambda_i, \tau) p(\lambda_i \mid \tau) p(\tau) d\lambda_i
\end{align*}
Here $\tau$ is a global mixing parameter and $\lambda_i$'s are the local mixture ones. In many cases, we also model $\tau \sim p(\tau)$. There is great interest in being able to analytically calculate the marginal distribution, $p(x_i)$, of a global-local mixture. Primarily as a log-penalty, $\phi(x_i) = -\log p(x_i)$, in a sparse inference problem we show how two simple integral identities, namely Schl\"omilch and Liouville integrals, derive useful `closed-form' identities very quickly. Moreover. it provides a framework for generating new random variables via the transformation $Y = a X - b X^{-1}$ for hyper-parameters $a$ and $b$. It also provides a transformation framework that links together different global-local mixtures. 

We start by stating the two key integral identities that we shall use throughout the Cauchy-Schl\"omilch transformation: 
\begin{equation}
\int_0^\infty f \left\{ ( a x - b x^{-1} )^2 \right\} d x = \frac{1}{2a} \int_0^\infty f(y^2) d y \label{eq:identity}
\end{equation}
and the Liouville transformation:
\begin{equation}
\int_{0}^{\infty} f\left(ax + \frac{b}{x} \right) \frac{dx}{\sqrt{x}} = \frac{1}{\sqrt{a}} \int_{0}^{\infty} f \left( 2\sqrt{ab} + y \right) \frac{dy}{\sqrt{y}}, a,b >0 \label{eq:liouville}
\end{equation}
See \citep{boros2006irresistible,baker2008probabilistic,amdeberhan2010cauchy,jones2014generating} for a detailed discussion of these identities. 

\begin{proof}
Equation \eqref{eq:identity} follows from the simple transformation $t = b/ax$: 
\begin{equation*}
  I = \int_{0}^{\infty} f \left\{(ax - b/x)^2 \right\} dx = \int_{0}^{\infty} f \left\{(at - b/t)^2 \right\} \frac{b}{at^2}.
\end{equation*}
Now, adding we get: 
\begin{align*}
2 I & = \int_{0}^{\infty} f \left\{(at - b/t)^2 \right\} \left( 1+\frac{b}{at^2} \right) dt.
\end{align*}
Finally transforming $y = b/t - at$ implies $dy = -a (1+b/at^2)$, which yields $I = (2a)^{-1} \int_{0}^{\infty} f(y^2) dy$ as required. 
\end{proof}
The proof for the Liouville transformation follows in a similar manner which we omit for the sake of brevity. 

A useful generalization of the Cauchy-Schl\"omilch transformation is: 
\begin{equation}
  \int_0^\infty f \left[ \{x-g(x)\}^2 \right] dx = \int_0^\infty f( y^2 ) dy \label{eq:gen}
\end{equation}
where $g(x)=g^{-1}(x)$ is a self-inverse function such as $g(x) = b/x$ or $g(x) = -a^{-1}\log\{1-\exp(a x)\}$, see \citet{amdeberhan2010cauchy} for a detailed discussion. %The proof is along the same lines and we skip it for the sake of brevity. 

\section{Global Local Scale Mixture}
\subsection{Lasso as a Normal Scale Mixture}
It is well known that the double exponential or Laplace distribution arises as a normal scale mixtures with a Gamma mixing density \citep{andrews1974scale}. A simple transformation proof follows from the \CS formula where, $ f(x) = e^{-x} $ in \eqref{eq:identity}. The normal integral identity, $ \int_{0}^{\infty} f(y^2) dy = \int_0^\infty e^{-y^2} d y = \sqrt{\pi}/2 $ becomes $\int_{0}^{\infty} f\{(ax-bx^{-1})^2\} dx$, namely,
$$
\int_0^\infty e^{- a^2 x^2 - b^2 / x^2 } d x = \int_0^{\infty} e^{-ab \left( \frac{a}{b} x^2 + \frac{b}{a}x^{-2} \right)} dx =  \frac{\sqrt{\pi}}{2a} e^{- 2 ab}
$$
Substituting $ t = (a/b)^{1/2} x $ and $c = ab$ we get the classic \citet{andrews1974scale} result for double exponential (lasso) penalty.  
\begin{align*}
  \int_0^\infty e^{- c (t - t^{-1})^2} d t & = \half (\pi/c)^{1/2} \Rightarrow \int_0^\infty e^{- c (t^2 + t^{-2})} d t = \half (\pi/c)^{1/2} e^{-2c} %\label{eq:andrews}
\end{align*}
The advantage of this short proof is that the Laplace density can be viewed as a transformation of the normal, as $y = t - t^{-1}$ in the above equation leads back to the normal density.

\begin{remark}
%(Need to check this carefully!) 
The usual identity for lasso is the following proved by \citet{levy1940certains}.
\beq
\int_{0}^{\infty} \frac{a}{\sqrt{2\pi t^3}} e^{-a^2/2t} e^{-\lambda t} dt = e^{-a\sqrt{2\lambda}} \label{eq:levy}
\eeq
%\end{remark}
%Must apply to other exponential family mixtures? $ f(x ) = x^{\alpha-1} e^{-x} $ etc.
%\begin{remark} 
For $a = 1/2$, the above can be written as: 
\beq
E \left[\exp\{-\lambda^2/4 G \} \right] = \exp(-\lambda), \; \mbox{where } G \sim \mbox{Ga} (1/2, 1/2) \label{eq:gamma}
\eeq 
\end{remark}
\begin{proof}
The first relationship can be proved by substituting $t^{-1} = x^2$, which makes the left hand side in \eqref{eq:levy} equal to: 
\begin{align*}
\int_{0}^{\infty} \frac{a}{\sqrt{2\pi t^3}} e^{-a^2/2t} e^{-\lambda t} dt & = \sqrt{\frac{2}{\pi}} a e^{-a\sqrt{2\lambda}} \int_0^{\infty} e^{-\left(\frac{a}{\sqrt{2}} x - \lambda x^{-1}\right)^2} dx \\
& = \exp(-a\sqrt{2\lambda}).
\end{align*}
The last step follows from a direct application of the \CS formula. For the second relationship \eqref{eq:gamma}, fixing $a = 1$ and substituting $t = x^{-1}$ yields: 
$$
\int_{0}^{\infty} \frac{a}{\sqrt{2\pi t^3}} e^{-a^2/2t} e^{-\lambda t} dt = \int_{0}^{\infty} e^{-\lambda / x} \sqrt{\frac{1}{2\pi}} x^{-\half} e^{-\half x} dx, 
$$
where the left hand side can be identified as $E \left[\exp\{-\lambda^2/4 G \} \right]$ for $G \sim \mbox{Ga}(1/2,1/2)$. \qedhere
\end{proof}

\subsection{Logit and Quantile as Global-local Mixtures}
Logistic modeling can be viewed as a global-local mixture via the \PG distribution \citep{polson2013bayesian}. This leads to efficient MCMC algorithms for inference. The two key marginal distributions for the hyperbolic-GIG \citep{barndorff1977infinite} and Z-\Polya mixtures \citep{polson2013bayesian,barndorff1982normal} are 
\begin{align}
\frac{\alpha^2-\kappa^2}{2\alpha} e^{-\alpha|x-\mu| + \kappa(x-\mu)} & = \int_0^{\infty} \phi(x \mid \mu + \kappa \lambda, \lambda) p_{GIG}(\lambda \mid 1,0,\sqrt{\alpha^2-\kappa^2}) (\lambda)  d\lambda \label{eq:GIG}\\
\frac{1}{B(\alpha,\kappa)} \frac{e^{\alpha(x-\mu)}}{(1+e^{x-\mu})^{\alpha + \kappa}} & = \int_0^{\infty} \phi( x \mid \mu + \kappa \lambda, \lambda) p_{Polya}(\lambda \mid \alpha,\kappa) (\lambda) d\lambda \label{eq:polya}
\end{align}
where $\phi(\mu + \kappa \lambda, \lambda)$ denotes a normal density. The corresponding local mixture distributions are Generalized Inverse-Gaussian and the \Polya-Z denoted by $p_{GIG}$ and $p_{Polya}$ respectively. Rather surprisingly, the logit and quantile identities can be derived from the \CS transformation \eqref{eq:identity}. We give the proofs below: 

\begin{lemma}
The logistic and quantile mixtures admit a global-local mixture representation via the \CS transformation in \eqref{eq:identity}. 
\end{lemma}
\begin{proof}
%\noindent \textbf{Proof of \eqref{eq:GIG}} \\
To prove \eqref{eq:GIG}, let $f(x) = e^{-x^2/2}$, $a = \alpha, b = |x-\phi|$ in \eqref{eq:identity}, then we have: 
$$
\sqrt{\frac{2}{\pi}} \int_{0}^{\infty} e^{-\half \left(\alpha y - \frac{|x-\mu|}{y} \right)^2} dy = \frac{1}{\alpha}\frac{1}{\sqrt{2\pi}} \int_0^{\infty} e^{-\half y^2} dy = \frac{1}{\alpha}
$$
Now letting $\nu = y^2$ and re-arranging the constant terms, we get the relation:
$$
\frac{1}{\alpha} e^{-\alpha|x-\mu|} = \int_{0}^{\infty} e^{-\left( \frac{(x-\mu)^2}{2\nu} + \frac{\alpha^2}{2} \nu \right)} \frac{1}{\sqrt{2\pi\nu}} d\nu.
$$
Multiplying both sides by $2^{-1}(\alpha^2-\kappa^2) \exp\{\kappa(x-\mu)\}$, re-arranging terms to complete squares, to yield 
\begin{equation*}
  \frac{\alpha^2-\kappa^2}{2\alpha} e^{-\alpha|x-\mu| + \kappa(x-\mu)} = \int_0^{\infty} \phi(x \mid \mu + \kappa \nu, \nu) \frac{\alpha^2-\kappa^2}{2} e^{-\frac{\alpha^2-\kappa^2}{2} \nu} d \nu. 
\end{equation*}
The mixing distribution on the right hand side is the exponential distribution with rate parameter $(\alpha^2-\kappa^2)/2$, which is a special case of the Generalized inverse Gaussian (or GIG) distribution. Etienne Halphen circa 1941 \citep{seshadri1997halphen} introduced the GIG and \citet{barndorff1977infinite} studied its properties. The density with parameters $(\lambda, \delta, \gamma)$ has the form: 
$$
p_{GIG}(x \mid \lambda, \delta, \gamma) = \frac{(\gamma/\delta)^{\lambda}}{2K_{\lambda}(\delta \gamma)} x^{\lambda-1} \exp \left\{ -\half (\delta^2 x^{-1} + 
\gamma^2 x )  \right\}; \; x > 0
$$
where $K_{\lambda}$ is the modified Bessel function of the second kind. The Liouville formula directly applied here immediately shows its a probablity density function. 

When $\delta$ or $\gamma$ is zero, the normalizing constant is to be replaced by the corresponding limits as $K_{\lambda}(u) \sim \Gamma(|\lambda|)2^{|\lambda|-1} u^{|\lambda|}$ when $\lambda \neq 0$. It turns out that if $\delta=0$, GIG is identical to a Gamma distribution with density 
$$
p_{GIG}(x \mid \lambda, \delta = 0 , \gamma) = \frac{(\alpha)^{\lambda}}{\Gamma(\lambda)} x^{\lambda-1} \exp\{ -\alpha x \}; \; x > 0, \alpha = \gamma^2 / 2 
$$
%\end{proof} 
%
%%%%%%%%%%%
%\begin{proof}
%\noindent \textbf{Proof of \eqref{eq:polya}} \\
Next we present a simple proof for the \PG mixture in \eqref{eq:polya}. First, write $\kappa$ for $a-b/2$: 
\begin{equation}
  \frac{(e^{\psi})^a}{(1+e^{\psi})^b} = 2^{-b} e^{\kappa \omega} \int_0^{\infty} e^{-\omega \psi^2/2} p(\omega) d\omega \label{eq:pg}
\end{equation}
where $\omega \sim PG(b,0)$, the \PG distribution with density given by: 
$$
p(x \mid b, 0) = \frac{2^{(b-1)}}{\Gamma(b)} \sum_{n=0}^{\infty} (-1)^n \frac{\Gamma(n+b)}{\Gamma(n+1)} \frac{2n+b}{\sqrt{2\pi x^3}} e^{-\frac{(2n+b)^2}{8x}} 
$$
The logit function corresponds to $a=0,b=1$ in \eqref{eq:pg}. The \CS identity then simplifies to:  
\begin{equation}
  \frac{1}{1+e^{\psi}} = \half e^{-\half \psi} \int_0^{\infty} e^{-\frac{\psi^2}{2} \omega} p(\omega) d\omega 
  \text{ where } p(\omega) = \sum_{n=0}^{\infty} (-1)^n \frac{2n+1}{\sqrt{2\pi \omega^3}} e^{-\frac{(2n+1)^2}{8\omega}}
  \label{eq:logit}
\end{equation}
We will now prove that the right hand side equals the left hand side in \eqref{eq:logit}. To do this, write the left-hand side as:
\begin{align*}
I & = \half e^{-\psi/2} \int_0^{\infty} e^{-\frac{\psi^2}{2} \omega} \sum_{n=0}^{\infty} (-1)^n \frac{2n+1}{\sqrt{2\pi \omega^3}} e^{-\frac{(2n+1)^2}{8\omega}}d \omega \\
& = \half e^{-\psi/2}  \sum_{n=0}^{\infty} (-1)^n \frac{2n+1}{\sqrt{2\pi}} \int_0^{\infty} e^{- \left( \frac{\psi^2}{2}  \omega + \frac{(2n+1)^2}{8\omega} \right) } \frac{1}{\sqrt{ \omega^3}} d\omega. 
\end{align*}
Using the change of variable $\omega = t^{-2}$, we get 
\begin{align*}
I & = e^{-\psi/2}  \sum_{n=0}^{\infty} (-1)^n \frac{(2n+1)}{\sqrt{2\pi}} \int_{0}^{\infty} e^{-\left( \frac{\psi^2}{2t^2} + \frac{(2n+1)^2 t^2}{8} \right)} d t \\
& = \sum_{n=0}^{\infty} (-1)^n \left[  e^{-(n+1)\psi} \frac{(2n+1)}{\sqrt{2\pi}} \left\{ \int_{0}^{\infty}e^{-\half \left( \frac{(2n+1)t}{2} - \frac{\psi}{t}\right)^2 } dt \right\} \right].
\end{align*}
Now, apply \CS transformation to the integral within curly brackets to obtain: 
$$ 
\int_{0}^{\infty}e^{-\half \left( \frac{(2n+1)t}{2} - \frac{\psi}{t}\right)^2 } dt = \int_0^{\infty} e^{-\half y^2} dy \frac{1}{2n+1} = \frac{\sqrt{2\pi}}{2n+1}
$$
Putting things back together, we arrive at the logit function: 
$$
I = \sum_{n=0}^{\infty} (-1)^n e^{-(n+1)\psi} = \frac{1}{1+e^{\psi}}.
$$
\end{proof}

An alternative proof using Laplace transformation is provided in \cite{polson2013bayesian}. 
\begin{remark}
In the special case $\alpha = \kappa$, Equation \eqref{eq:GIG} and the limiting result yields the following identity: 
$$
(\alpha^2-\kappa^2)^{-1}p_{GIG}(1,0,\sqrt{\alpha^2-\kappa^2}) \equiv 1
$$
Hence it is as if the latent variable has a marginal improper uniform prior $p(\lambda) = 1, \forall \lambda \in \Re$. We can also write the result as: 
\begin{equation}
  \int_{0}^{\infty} \phi(b \mid -a\lambda, c\lambda) d\lambda = a^{-1} \exp(-2 \max(ab/c,0)) \label{eq:svm}
\end{equation}
This is useful in support vector machines \cite{polson2011data}.
\end{remark}

\begin{remark}
In a discussion of \citet{polson2011data}, \citet{hans2011comment} pointed out that the elastic-net regression can be recast as a normal mean variance mixture problem where the mixing density belongs to a `orthant-normal' family of distributions. The orthant-normal prior on a single regression coefficient $\beta$ given hyper-parameters $\lambda_1$ and $\lambda_2$ is given by: 
\[
p (\beta \mid \lambda_1, \lambda_2)  = 
  \begin{cases} 
   \phi(\beta \mid \frac{\lambda_1}{2\lambda_2}, \frac{\sigma^2}{\lambda_2}) / 2\Phi(\frac{-\lambda_1}{2\sigma\sqrt{\lambda_2}}) & \text{if } \beta < 0 \\
   \phi(\beta \mid \frac{-\lambda_1}{2\lambda_2}, \frac{\sigma^2}{\lambda_2}) / 2\Phi(\frac{-\lambda_1}{2\sigma\sqrt{\lambda_2}})       & \text{if } \beta \geq 0
  \end{cases} \label{eq:hans}
\]
\citet{hans2011comment} then proves the following theorem: 
\begin{theorem}
Under the orthant normal prior on $\beta$ given above and prior on $\lambda_2$ with the density
$$
p(\lambda_2 \mid \lambda_1, \sigma^2) = \frac{\lambda_1^2}{2\sigma^2\lambda_2^2} \Phi \left( \frac{-\lambda_1}{2\sigma \sqrt{\lambda_2}} \right), \lambda_2 > 0 
$$
the induced marginal prior on $\beta$ is a double-exponential, in particular, $(\beta \mid \lambda_1, \sigma^2) \sim \mathrm{DE}(\lambda_1/\sigma^2)$, where $\mathrm{DE(\lambda)}$ denotes the double-exponential distribution with rate parameter $\lambda$. 
\end{theorem}
This result comes as a corollary of \eqref{eq:svm}. 

%the limiting result stated in the last remark, i.e. it follows from the identity 
%$$
%\int_{0}^{\infty} \phi(b \mid -a\lambda, c\lambda) d\lambda = a^{-1} exp(-2 \max(ab/c,0)).
%$$
\end{remark}
%\subsection{Stable Laws}
%The symmetric stable distribution is defined by its characteristic function $\phi(t) = \exp\{ -|t|^{\alpha} \}$, with exponent $\alpha \in (0,2]$. The symmetric stable distribution also admits a normal scale mixture representation as where the mixing density is given by: 
%$$
%f(v) = \half s_{\alpha/2} \left( \frac{v}{2} \right), v > 0 
%$$
%where $s_{\alpha/2}$ is the density of the positive stable distribution with index $\alpha / 2$ (Feller, 1971). This result can also shown to be a consequence of the integral identity \eqref{eq:identity}. 
%\textit{I am still working on the proof of it.}

\section{Transformations of Scale Distribution} 

\cite{jones2014generating} characterizes the densities of the form $f(x) = 2g\{ t(x) \}$ and provided conditions for $t(\cdot)$ for $f(\cdot)$ to be a density. This result allows us to generate new distributions starting from a baseline `simple' distribution and transforming the scale by a suitable function. The main result is quoted below: 
\begin{proposition}\label{prop:jones}
Let $\Pi: \mathcal{D} \to \mathcal{S}_{f}$ be a piecewise differentiable monotone increasing function with inverse $t$, where $\mathcal{D} \supset \mathcal{S}_{g} \ni 0$. Suppose that 
$$
\Pi(y) - \Pi(-y) = y, \text{ for all } y \in \mathcal{D}
$$
If $g(x)$ is a density on $\mathcal{S}_{g}$ symmetric about zero, then 
$$
f(x) = 2g \{ t(x) \} \equiv 2g \{ \Pi^{-1}(x) \}
$$
 is a density on $\mathcal{S}_{f}$.
\end{proposition}
Curiously, an equivalent formulation of $t(x)$ is that it should have the form $x-s(x)$ where $s : \Re^+ \to \Re^+$ is an onto monotone decreasing function that is self-inverse, i.e. $s\{ s(x)\} = x$. This together with the \CS transformation \eqref{eq:gen} guarantees that the left hand side is a density on the appropriate domain, and rather surprisingly, provides for a way to represent the resulting $g\{t(x)\}$ as a global-local scale mixture! 
 
Furthermore, \cite{jones2014generating} identifies that only a few choices of $\pi(\cdot)$ leads to fully tractable formulae for its integral $\Pi(y) = \int_{-\infty}^{y} \pi(\omega) d\omega$ and its inverse $t = \Pi^{-1}$. Two special choices are the $t$ distribution with 2 degrees of freedom and the logistic. 
\begin{align}
t(2): \Pi_{T}(y) = (1/2)(y+\sqrt{4b+y^2}) & \Rightarrow \Pi_T^{-1}(x) = t_T(x) = x - (b/x) \\
Logistic: \Pi_{L}(y) = a^{-1} \log(1+e^{ay}) & \Rightarrow \Pi_L^{-1}(x) = t_L(x) = a^{-1} \log(e^{ax}-1) 
\end{align}
Now, we can use these results to generate new probability distributions with different choices of `simple' baseline function $g(\cdot)$ and derive new scale mixture representations that are useful in Bayesian global-local modeling. 

%\begin{remark} 
\subsection{Symmetric and R-symmetric distributions}

For absolutely continuous random variables supported on the positive half-line $\Re^{+}$, the density function $f(\cdot)$ has reciprocal symmetry (R-symmetry) if $f(\theta y) = f(\theta / y)$ for all $y > 0$ and some $\theta >0$ (Mudholkar and Wang, 2007). It follows from the integral identity \eqref{eq:identity} that if $f(x), x \geq 0$ is a density function, so is $g(x) = 2a f(|ax-b/x|), x >0$, and $f(\cdot)$ and $g(\cdot)$ are called the mother and the daughter pdf. As \cite{chaubey2010reciprocal} pointed out, there is an one-to-one correspondence between $f$ and $g$, and furthermore if $f(x)$ is the pdf of a symmetric real-valued random variable $Y$, the daughter pdf $g(x) = f(x-1/x), x>0$ is an R-symmetric density, and vice-versa, there exists a symmetric density $f(x) = g(x+\sqrt{1+x^2})$ for every R-symmetric density $g(x)$. Furthermore, $f(\cdot)$ is unimodal if and only if $g(\cdot)$ is unimodal. \cite{chaubey2010reciprocal} provides a few examples of generating R-symmetric densities $g$ starting from well-known symmetric densities $f$. The most well-known example of this duality is perhaps the normal density as $f$ that gives rise to the root reciprocal inverse Gaussian, abbreviated as RRIG, distribution, with density given by: 
$$
g(x) = \sqrt{\frac{2\lambda}{\pi}} \exp \left\{ - \frac{\lambda}{2} \left( x - \frac{1}{x} \right)^2 \right\}, x >0.
$$
Once again, the \CS transformation with $y = x - x^{-1}$ immediately shows its a density. 

\section{Discussion}

Apart from providing simple proofs for well-known normal scale mixture representations, the main motivation behind studying properties of the integral identities is twofold: we can generate new distributions by a suitable scale transformation $f(x) = 2g\{ t(x) \}$ of a `simple' baseline function $f$ under some conditions, and for $t(x) = x - 1/x$, we get R-symmetric densities on $\Re^+$ from well-known symmetric densities and vice-versa, and given a density $f(x)$ we can create a new global-local scale family $f(ax-bx^{-1})$, by reallocating its probability mass. 

Khintchine's theorem for unimodality of univariate distributions provides a useful tool for generating univariate and multivariate random variables \citep{bryson1982constructing}. Khintchine's theorem states that any random variable $X$ with a mode at zero can be written as a product $X = ZU$, where $U \sim U(0,1)$ and $Z$ has the density function $f_Z(z) = -zf_{X}'(z)$. \citep{bryson1982constructing} and successively \cite{jones2010distributions,jones2012khintchine} discuss how Khintchine's theorem allows us to construct both univariate and multivariate distributions, the latter with special dependence structure. \cite{jones2014generating} develops an extended Khintchine's theorem that further lets one generate random variable with unimodal density of the form $2g(t(x))$ discussed before in Proposition \ref{prop:jones}. 

The \CS transformation not only guarantees an `astonishingly simple' normalizing constant for $f(\cdot)$, it also establishes the wide class of unimodal densities as global-local scale mixtures. As we have discussed before, the global-local scale mixtures with conditional Gaussianity hold a special place in Statstical literature, as these models can be rapidly fit using an expectation-maximization algorithm as pointed out by \cite{polson2013data}. This has been extended in a $2011$ unpublished note by Palmer, Kreutz-Delgado and Makeig who have provided a tool for modeling multivariate dependence by writing general non-Gaussian multivariate densities as multivariate Gaussian scale mixtures. Our future goal is to extend the \CS transformation to express the wide multivariate Gaussian scale mixture models as global-local mixtures that also facilitate easy computation. \par

We end our paper with conjectures that two other remarkable identities arise as corollaries of the \CS transformation. The first one is a recent result by \cite{zhang2014uniform} that proves the uniform correlation mixture of the bivariate Gaussian density with unit variance is a function of the maximum norm: 
\begin{equation}
  \int_{-1}^{1} \half \frac{1}{2\pi\sqrt{1-\rho^2}} \exp \left\{ - \frac{x_1^2 + x_2^2 - 2 \rho x_1 x_2}{2(1-\rho^2)} \right\} d \rho = 
  \half (1- \Phi(\vectornorm{x}_{\infty})) \label{eq:bivar}, 
\end{equation}
where $\Phi(\cdot)$ is the standard normal distribution function and $\vectornorm{x}_{\infty} = \max \{ x_1, x_2\}$. The bivariate density on the right side of \eqref{eq:bivar} was introduced before in \cite{bryson1982constructing} as uniform mixtures of a $\chi_3$ random variate, but the representation as a uniform correlation mixture is a surprising new find. The second candidate is the symmetric stable distribution, defined by its characteristic function $\phi(t) = \exp\{ -|t|^{\alpha} \}; \alpha \in (0,2]$, also admits a normal scale mixture representation as where the mixing density is: 
$$
f(v) = \half s_{\alpha/2} \left( \frac{v}{2} \right), v > 0 
$$
where $s_{\alpha/2}$ is the density of the positive stable distribution with index $\alpha / 2$ (Feller, 1971). An important application of this is the Bayesian bridge regression by \cite{polson2014bayesian}, where the regularization is an outcome of a scale mixture of normal distributions with respect to an $\alpha$-stable random variable. We conjecture that these two results follow as upshots of the \CS formula \eqref{eq:identity}. Other fruitful areas could be unearthed by applications of the Liouville formula to recognize and generate global-local mixtures, and other applications such as calculating higher-order `closed-form' moments $E(X^n)$ for random variables $X$ that admit a global-local representation. 

%%%%%%%
%\end{remark}
\bibliographystyle{apa}
\bibliography{glref}
\end{document}
